% (c) 2002 Matthew Boedicker <mboedick@mboedick.org> (original author) http://mboedick.org
% (c) 2003-2007 David J. Grant <davidgrant-at-gmail.com> http://www.davidgrant.ca
% (c) 2008 Nathaniel Johnston <nathaniel@nathanieljohnston.com> http://www.nathanieljohnston.com
% (c) 2011 Scott Clark <sc932@cornell.edu> http://cam.cornell.edu/~sc932
%

%This work is licensed under the Creative Commons Attribution-Noncommercial-Share Alike 2.5 License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-sa/2.5/ or send a letter to Creative Commons, 543 Howard Street, 5th Floor, San Francisco, California, 94105, USA.

\documentclass[letterpaper,11pt]{article}
\newlength{\outerbordwidth}
\pagestyle{empty}
\raggedbottom
\raggedright
\usepackage[svgnames]{xcolor}
\usepackage{framed}
\usepackage{tocloft}
\usepackage{etoolbox}
\usepackage{verbatim}
\robustify\cftdotfill

%-----------------------------------------------------------
%Edit these values as you see fit
\setlength{\outerbordwidth}{3pt}  % Width of border outside of title bars
\definecolor{shadecolor}{gray}{0.75}  % Outer background color of title bars (0 = black, 1 = white)
\definecolor{shadecolorB}{gray}{0.93}  % Inner background color of title bars

%-----------------------------------------------------------
%Margin setup
\setlength{\evensidemargin}{-0.25in}
\setlength{\headheight}{-0.25in}
\setlength{\headsep}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}
\setlength{\tabcolsep}{0in}
\setlength{\textheight}{9.75in}
\setlength{\textwidth}{7in}
\setlength{\topmargin}{-0.3in}
\setlength{\topskip}{0in}
\setlength{\voffset}{0.1in}

%-----------------------------------------------------------
%Custom commands
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\resheading}[1]{\vspace{8pt}
  \parbox{\textwidth}{\setlength{\FrameSep}{\outerbordwidth}
    \begin{shaded}

\setlength{\fboxsep}{0pt}\framebox[\textwidth][l]{\setlength{\fboxsep}{4pt}\fcolorbox{shadecolorB}{shadecolorB}{\textbf{\sffamily{\mbox{~}\makebox[6.762in][l]{\large #1} \vphantom{p\^{E}}}}}}
    \end{shaded}
  }\vspace{-5pt}
}

\newcommand{\ressubheading}[4]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{#3} & \textit{#4} \\
\end{tabular*}\vspace{-6pt}}

\newcommand{\ressubheadingtwo}[2]{
\begin{tabular*}{6.5in}{l@{\cftdotfill{\cftsecdotsep}\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
\end{tabular*}\vspace{-6pt}}

\renewcommand\labelitemiii{$\circ$}

%-----------------------------------------------------------
\begin{document}

\begin{tabular*}{7in}{l@{\extracolsep{\fill}}r}

\textbf{\Large Abhishek Mahurkar} & \textbf{\today} \\
\texttt{Software Engineer at Snapdeal} & \texttt{amabhishek25@gmail.com} \\
\texttt{www.linkedin.com/in/networkam007} & \texttt{+91-9975039387}

\end{tabular*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Education}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Visvesvaraya National Institute of Technology}{Nagpur, IN}{B.Tech. Computer Science and Engineering}{2011 - 2015}
	\begin{itemize}
		\resitem{Graduated with a 7.06/10 CGPA}
		\begin{comment}
		\resitem{Data Structures and Algorithms, Information Retrieval, Cloud Computing}
		\end{comment}
	\end{itemize}

\item
	\ressubheading{Somalwar Junior College Ramdaspeth}{Nagpur, IN}{Higher Secondary School Certificate (State Board). Electronics}{2011}
	\begin{itemize}
		\resitem{Passed Higher Secondary with Grade I Distinction 90.17\%}
	\end{itemize}
	
\item
	\ressubheading{St. Francis De'Sales High School}{Nagpur, IN}{Secondary School Certificate (State Board)}{2009}
	\begin{itemize}
		\resitem{Passed Secondary School with Distinction 91.23\%}
	\end{itemize}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Skills}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item {\bf Development:} JAVA, C/C++, Android, HTML, CSS, JavaScript

\item {\bf Technology:} Spring Framework, linux, git, vim

\item {\bf Database:} Aerospike, Cassandra, ElasticSearch, MongoDB, MySQL

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Work Experience}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
	\ressubheading{Snapdeal}{Bengaluru, IN}{Software Development Engineer (User Generated Content Team)}{July 2015 - current}
	 
	
	\begin{itemize}
            \resitem{{\bf Reviews and Ratings:} R\&R System, Image Reviews, Reviews Moderation Panel, Data Syncing/Cleaning Utilities }
            \begin{itemize}
            	\resitem{Developed Framework for removing non Buyer reviews,fraud ratings to increase the trust of R\&R content}
            	\resitem{Worked on implementing image review,attribute level rating features on Android app}
            \end{itemize}
            \resitem{{\bf Questions and Answers:} Q\&A System, Q\&A Moderation Panel, Moderation Framework }
            \begin{itemize}
            	\resitem{Implemented new features on Moderation Panel which improved productivity of Moderators}
            	\resitem{Developed Framework for moderating content based on keywords which helped in automating moderation of some content }
            \end{itemize}
            \resitem{ Worked extensively on backend tasks of both the systems such as developing and optimising API's, Bug fixing }
            \resitem{ Improved caching strategy to reduce cache memory usage, developed cache warm-up utility}
            \resitem{ Technologies : JAVA, Aerospike, ElasticSearch, Cassandra, MongoDB, Kafka}
	\end{itemize}
\begin{comment}
\item
	\ressubheading{Bloomberg LP}{New York, NY}{Financial Software Development Intern}{Summer 2011}
	\begin{itemize}
		\resitem{Developed end-to-end reporting software in \texttt{C++} and \texttt{javascript}}
    \resitem{Implemented statistical models to perform forward and backward portfolio analysis}
	\end{itemize}

\item
	\ressubheading{DOE Joint Genome Institute (Lawrence Berkeley National Lab)}{Walnut Creek, CA}{Researcher in Analysis Group under Dr. Zhong Wang}{Summer 2010}
	\begin{itemize}
		\resitem{Created \textbf{open source} genome validation software tool in \texttt{python} and \texttt{C} (alescore.org)}
    \resitem{Used machine learning to mine TBs of genome data efficiently using novel likelihood function}
	\end{itemize}

\item 
	\ressubheading{Los Alamos National Laboratory}{Los Alamos, NM}{Researcher in Metagenomics Group under Dr. Nick Hengartner}{Summer 2009}
	\begin{itemize}
		\resitem{Wrote \textbf{open source} alignment algorithm software tool in \texttt{python}, \texttt{C} and \texttt{CUDA}}
    \resitem{Used statistical models to discover sequence alignments using parallel algorithms on GPUs}
	\end{itemize}

\item
	\ressubheading{Oregon State University}{Corvallis, OR}{Research Assistant under Prof. Malgorzata Peszynska and Prof. Rubin Landau}{2005-2008}
	\begin{itemize}
		\resitem{Finite element analysis with uncertainty and web-based teaching in \texttt{Java}}
	\end{itemize}

\item
	\ressubheading{Max Plank Institute for the Physics of Complex Systems}{Dresden, Germany}{NSF REU Research Assistant under Prof. Steven Tomsovic}{Summer 2007}
	\begin{itemize}
		\resitem{Research on extreme value statistics in \texttt{MATLAB} and \texttt{FORTRAN}}
	\end{itemize}

\item
	\ressubheading{University of California: Davis}{Davis, CA}{NSF REU Research Assistant under Prof. Daniel Cox}{Summer 2006}
	\begin{itemize}
		\resitem{Computational biophysics research as applied to protein folding in \texttt{Java}}
	\end{itemize}

\end{comment}

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\resheading{Academic Projects}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{itemize}

\item
    \ressubheading{Trip Advisor (\texttt{github.com/repoleved25/TripAdvisor})}{JAVA, Android, MySQL, AWS}{Application for planning trips to new city}{Jan 2015 - May 2015}
    \begin{itemize}
        \resitem{Designed and developed trip advisor application for users which helps them to plan trip on their visit to new city with auto generated packages.}
	\resitem{Implemented the user application for android smartphones and the backend was deployed on AWS cloud platform.}
        \end{itemize}
        
\item
	\ressubheadingtwo{Employee Database System} {April 2013}
	\begin{itemize}
	      	\resitem{Created an employee database application which provided various operations such as CRUD using B-Tree as database. This project was implemented in C}
	\end{itemize}


\begin{comment}

\item
    \ressubheading{MOE: Metric Optimization Engine (\texttt{github.com/Yelp/MOE})}{Python, C++, CUDA}{A global, black box optimization engine for real world metric optimization}{2010 - Current}
    \begin{itemize}
        \resitem{Implemented throughout Yelp, optimizing ad metrics. 2nd most popular open source project.}
        \resitem{Talk: \texttt{bit.ly/1plYZA2}, Slides: \texttt{slidesha.re/1zOrOJy}, Blog: \texttt{bit.ly/1x73xdr}}
        \resitem{Presented to executives, universities, conferences and companies around the country.}
	\end{itemize}

\item
    \ressubheading{My Resume/CV (\texttt{github.com/sc932/resume})}{\LaTeX}{This resume and my CV.}{2010 - current}
    \begin{itemize}
        \resitem{280+ GitHub stars, previous \#1 article on Hacker News, 60+ forks.}
	\end{itemize}

\item
    \ressubheading{ALE: Assembly Likelihood Estimator (\texttt{github.com/sc932/ALE})}{C, Python}{Probabilistic evaluation of genome assemblies}{2010 - 2013}
    \begin{itemize}
        \resitem{Uses statistical function to score and rank genome assemblies, published in Bioinformatics}
	\end{itemize}
	
\end{comment}

\end{itemize}

\begin{comment}
\resheading{Writing and Awards}

\begin{itemize}

\item {\bf Department of Energy Computational Science Graduate Fellow:} Four year full fellowship. $\sim$20 awarded nationally per year. Won the Communicating Science award (\texttt{bit.ly/VbcTZK}).
\item {\bf Yelp Blog:} Wrote several posts announcing the open sourcing of MOE, the Yelp Dataset Challenge and more. \texttt{bit.ly/1x73xdr}, \texttt{bit.ly/1oCCZvv}, \texttt{bit.ly/1sOsEBS}, \texttt{bit.ly/1plX7Hk}
\item {\bf Press:} WSJ: \texttt{on.wsj.com/VaOvqQ}, Cornell: \texttt{bit.ly/1oB2dzm},  DIEXIS: \texttt{bit.ly/1oofbl4}

\end{itemize}
\end{comment}

\end{document}
